Security Metrics for the Android Ecosystem

### 2016-04-11 dastats.tex
./update.sh

\newcommand{\daNumSigModels}{18}

@@

\newcommand{\daNumVulnsUsed}{11}

@@

\newcommand{\daOSMonthsOfData}{51}

@@

\newcommand{\daEndDate}{2015-09-22}

@@

\newcommand{\daNumManufacturers}{302}
\newcommand{\daNumSigManufacturers}{10}
\newcommand{\daNumModels}{2\,770}
\newcommand{\daNumOperators}{1\,470}
\newcommand{\daNumSigOperators}{14}
\newcommand{\daNumOSDevices}{20\,500}

@@

\newcommand{\daOSTotalDaysData}{1\,350\,000}
\newcommand{\daMeanInsecurityPercNominal}{87.3\%}
\newcommand{\daMeanInsecurityPerc}{$87.3 \pm 0.0\%$}
\newcommand{\daMeanInsecurityPercTwosfNominal}{87\%}
\newcommand{\daMeanInsecurityPercTwosf}{$87 \pm 0\%$}
\newcommand{\daMeanSecurityPercNominal}{12.7\%}
\newcommand{\daMeanSecurityPerc}{$12.7 \pm 0.0\%$}
\newcommand{\daMeanSecurityPercTwosfNominal}{13\%}
\newcommand{\daMeanSecurityPercTwosf}{$13 \pm 0\%$}
\newcommand{\daVulnFreeNominal}{0.127}
\newcommand{\daVulnFree}{$0.127 \pm 0.0$}
\newcommand{\daMeanOutstandingVulnerabilities}{$0.509 \pm 0.0$}
\newcommand{\daUpdatednessNominal}{0.0553}
\newcommand{\daUpdatedness}{$0.0553 \pm 0.0$}
\newcommand{\daUpdatednessPercNominal}{5.53\%}
\newcommand{\daUpdatednessPerc}{$5.53 \pm 0.0\%$}
\newcommand{\daUpdatednessPercTwosfNominal}{5.5\%}
\newcommand{\daUpdatednessPercTwosf}{$5.5 \pm 0.0\%$}
\newcommand{\daSecurityScoreNominal}{2.93}
\newcommand{\daSecurityScore}{$2.93 \pm 0.0$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{68.8\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$68.8 \pm 0.0\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{69\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$69 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{31.2\%}
\newcommand{\daCurrentMeanSecurityPerc}{$31.2 \pm 0.2\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{31\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$31 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.312}
\newcommand{\daCurrentVulnFree}{$0.312 \pm 0.002$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.0645 \pm 0.0$}
\newcommand{\daCurrentUpdatednessNominal}{0.0934}
\newcommand{\daCurrentUpdatedness}{$0.0934 \pm 0.0019$}
\newcommand{\daCurrentUpdatednessPercNominal}{9.34\%}
\newcommand{\daCurrentUpdatednessPerc}{$9.34 \pm 0.19\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{9.3\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$9.3 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{4.43}
\newcommand{\daCurrentSecurityScore}{$4.43 \pm 0.0$}
\newcommand{\daDailyParticipationNominal}{872}
\newcommand{\daDailyParticipation}{$872 \pm 271$}
\newcommand{\daNumFullVersions}{1\,300}
\newcommand{\daNumSigFullVersions}{101}
\newcommand{\daNumOSVersions}{50}
\newcommand{\daNumSigOSVersions}{28}
\newcommand{\daNumAPIVersions}{16}
\newcommand{\daNumFullVersionUpdates}{4\,670}
\newcommand{\daNumOSVersionUpdates}{3\,940}
\newcommand{\daUpdatesPerYearNominal}{1.27}
\newcommand{\daUpdatesPerYear}{$1.27 \pm 0.01$}
\newcommand{\daUpdatesPerYearTwosfNominal}{1.3}
\newcommand{\daUpdatesPerYearTwosf}{$1.3 \pm 0.0$}
\newcommand{\daNumFullOnlyVersionUpdates}{724}
\newcommand{\daNumSecurityUpdates}{1\,270}
\newcommand{\daNumPossibleSecurityUpdates}{2\,310}
\newcommand{\daOSCurveFitParamFirst}{83.6}
\newcommand{\daOSCurveFitParamSecond}{\num{0.0028}}
\newcommand{\daOSCurveFitRMSE}{0.114}
\newcommand{\daOSCurvePolyRMSE}{0.114}
\newcommand{\daOSCurveSplineRMSE}{0.114}

@@

\newcommand{\daOSCurveHalfDeployedYears}{$0.908 \pm 0.254$}

@@

\newcommand{\daOSCurveHalfDeployed}{$332 \pm 92$}
\newcommand{\daOSCurveFullDeployedYearsNominal}{3.16}
\newcommand{\daOSCurveFullDeployedYears}{$3.16 \pm 72$}
\newcommand{\daOSCurveFullDeployedNominal}{1\,150}
\newcommand{\daOSCurveFullDeployed}{$1\,150 \pm 265\,000$}
\newcommand{\daAPICurveFitParamFirst}{97.8}

@@

\newcommand{\daAPICurveFitRMSE}{0.11}
\newcommand{\daAPICurvePolyRMSE}{0.111}
\newcommand{\daAPICurveSplineRMSE}{0.111}
\newcommand{\daAPICurveHalfDeployedYearsNominal}{0.946}
\newcommand{\daAPICurveHalfDeployedYears}{$0.946 \pm 0.244$}
\newcommand{\daAPICurveHalfDeployedNominal}{345}
\newcommand{\daAPICurveHalfDeployed}{$345 \pm 89$}
\newcommand{\daAPICurveFullDeployedYearsNominal}{3.2}
\newcommand{\daAPICurveFullDeployedYears}{$3.2 \pm 7$}

@@

\newcommand{\daAPICurveFullDeployed}{$1\,170 \pm 265\,000$}
\newcommand{\daVulnAPKDuplicateFileOctoberPerc}{91.7\%}
\newcommand{\daVulnZergRushMonthsDefFixDeployed}{27.3}
\newcommand{\daTabSecScoresmanufacturer}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.24 \pm 0.00$ & $0.34 \pm 0.00$ & $0.60 \pm 0.01$ & $4.11 \pm 0.02$ \\  Motorola & $0.19 \pm 0.00$ & $0.12 \pm 0.00$ & $0.71 \pm 0.02$ & $3.11 \pm 0.02$ \\  Samsung & $0.13 \pm 0.00$ & $0.04 \pm 0.00$ & $0.58 \pm 0.00$ & $2.80 \pm 0.00$ \\  Sony & $0.14 \pm 0.00$ & $0.19 \pm 0.00$ & $1.09 \pm 0.02$ & $2.66 \pm 0.02$ \\  HTC & $0.14 \pm 0.00$ & $0.10 \pm 0.00$ & $0.86 \pm 0.01$ & $2.65 \pm 0.02$ \\  asus & $0.21 \pm 0.00$ & $0.51 \pm 0.01$ & $6.01 \pm 0.07$ & $2.38 \pm 0.02$ \\  other & $0.06 \pm 0.00$ & $0.05 \pm 0.00$ & $1.00 \pm 0.01$ & $2.02 \pm 0.02$ \\  alps & $0.03 \pm 0.00$ & $0.19 \pm 0.01$ & $3.99 \pm 0.08$ & $0.80 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.09 \pm 0.00$ & $5.00 \pm 0.05$ & $0.32 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.09 \pm 0.00$ & $6.00 \pm 0.08$ & $0.27 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table*}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{4.11}
\newcommand{\daSecScoreBestmanufacturerScore}{$4.11 \pm 0.0$}
\newcommand{\daSecScoreBestmanufacturerNumFullVersions}{142}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.273}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.273 \pm 0.007$}
\newcommand{\daSecScoreWorstmanufacturerNumFullVersions}{21}
\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.50 \pm 0.00$ & $0.54 \pm 0.01$ & $1.53 \pm 0.04$ & $4.70 \pm 0.04$ \\  Nexus 4 & $0.33 \pm 0.00$ & $0.82 \pm 0.01$ & $6.06 \pm 0.09$ & $3.78 \pm 0.04$ \\  Nexus 7 & $0.27 \pm 0.00$ & $0.73 \pm 0.01$ & $5.92 \pm 0.09$ & $3.29 \pm 0.04$ \\  other & $0.10 \pm 0.00$ & $0.14 \pm 0.00$ & $0.51 \pm 0.00$ & $3.08 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & $0.38 \pm 0.02$ & $2.91 \pm 0.04$ \\  HTC Sensation & $0.35 \pm 0.00$ & $0.01 \pm 0.01$ & $1.57 \pm 0.05$ & $2.44 \pm 0.05$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & $1.23 \pm 0.02$ & $2.27 \pm 0.02$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.06$ & $1.74 \pm 0.07$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $2.52 \pm 0.05$ & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $1.79 \pm 0.06$ & $0.90 \pm 0.05$ \\  GT-I9505 & $0.06 \pm 0.00$ & $0.13 \pm 0.00$ & $6.82 \pm 0.07$ & $0.62 \pm 0.01$ \\  GT-I9300 & $0.13 \pm 0.00$ & $0.01 \pm 0.00$ & $6.23 \pm 0.04$ & $0.57 \pm 0.01$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $3.03 \pm 0.05$ & $0.28 \pm 0.03$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & $6.93 \pm 0.08$ & $0.24 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $11.00 \pm 0.12$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}
\newcommand{\daSecScoreBestmodel}{Galaxy Nexus}
\newcommand{\daSecScoreBestmodelScoreNominal}{4.7}
\newcommand{\daSecScoreBestmodelScore}{$4.7 \pm 0.0$}
\newcommand{\daSecScoreBestmodelNumFullVersions}{49}

@@

\newcommand{\daSecScoreWorstmodelScore}{$0.0001 \pm 0.0272$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline nexus & $0.40 \pm 0.00$ & $0.49 \pm 0.00$ & $0.55 \pm 0.01$ & $5.28 \pm 0.02$ \\  non-nexus & $0.11 \pm 0.00$ & $0.03 \pm 0.00$ & $0.51 \pm 0.00$ & $2.76 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table*}}
\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.28 \pm 0.00$ & $0.12 \pm 0.00$ & $0.37 \pm 0.02$ & $3.91 \pm 0.03$ \\  T-Mobile & $0.22 \pm 0.00$ & $0.19 \pm 0.00$ & $0.39 \pm 0.01$ & $3.87 \pm 0.02$ \\  Orange & $0.22 \pm 0.00$ & $0.10 \pm 0.00$ & $0.36 \pm 0.02$ & $3.64 \pm 0.04$ \\  3 & $0.22 \pm 0.00$ & $0.09 \pm 0.00$ & $0.47 \pm 0.02$ & $3.45 \pm 0.03$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & $0.43 \pm 0.02$ & $3.41 \pm 0.03$ \\  Vodafone uk & $0.14 \pm 0.00$ & $0.13 \pm 0.00$ & $0.52 \pm 0.03$ & $3.19 \pm 0.04$ \\  AT\&T & $0.15 \pm 0.00$ & $0.08 \pm 0.00$ & $0.43 \pm 0.02$ & $3.17 \pm 0.02$ \\  unknown & $0.12 \pm 0.00$ & $0.20 \pm 0.00$ & $0.80 \pm 0.01$ & $2.95 \pm 0.02$ \\  Verizon & $0.19 \pm 0.00$ & $0.09 \pm 0.00$ & $0.82 \pm 0.02$ & $2.86 \pm 0.02$ \\  n Telenor & $0.05 \pm 0.00$ & $0.12 \pm 0.00$ & $1.14 \pm 0.02$ & $2.01 \pm 0.02$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & $1.44 \pm 0.03$ & $1.45 \pm 0.03$ \\  Grameenphone & $0.01 \pm 0.00$ & $0.04 \pm 0.00$ & $1.66 \pm 0.02$ & $1.10 \pm 0.01$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $2.08 \pm 0.04$ & $0.91 \pm 0.03$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.55 \pm 0.04$ & $0.55 \pm 0.02$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}
\newcommand{\daSecScoreBestoperator}{O2 uk}
\newcommand{\daSecScoreBestoperatorScoreNominal}{3.91}
\newcommand{\daSecScoreBestoperatorScore}{$3.91 \pm 0.0$}
\newcommand{\daSecScoreBestoperatorNumFullVersions}{103}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.547}
\newcommand{\daSecScoreWorstoperatorScore}{$0.547 \pm 0.017$}
\newcommand{\daSecScoreWorstoperatorNumFullVersions}{75}
\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & nexus \\ \hline equal & 0.0 & 0.0 & 0.0714 & 0.0 \\weight $m$ & 0.2 & 0.333 & 0.214 & 0.0 \\weight $u$ & 0.2 & 0.0 & 0.143 & 0.0 \\$f$ & 0.3 & 0.733 & 0.357 & 0.0 \\$m$ & 0.6 & 0.733 & 0.357 & 0.5 \\$u$ & 0.9 & 0.667 & 0.786 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}

>>>>

\newcommand{\daNumSigModels}{20}

@@

\newcommand{\daNumVulnsUsed}{14}

@@

\newcommand{\daOSMonthsOfData}{57}

@@

\newcommand{\daEndDate}{2016-03-13}

@@

\newcommand{\daNumManufacturers}{402}
\newcommand{\daNumSigManufacturers}{11}
\newcommand{\daNumModels}{3\,720}
\newcommand{\daNumOperators}{1\,650}
\newcommand{\daNumSigOperators}{18}
\newcommand{\daNumOSDevices}{24\,600}

@@

\newcommand{\daOSTotalDaysData}{1\,520\,000}
\newcommand{\daMeanInsecurityPercNominal}{83.1\%}
\newcommand{\daMeanInsecurityPerc}{$83.1 \pm 0.0\%$}
\newcommand{\daMeanInsecurityPercTwosfNominal}{83\%}
\newcommand{\daMeanInsecurityPercTwosf}{$83 \pm 0\%$}
\newcommand{\daMeanSecurityPercNominal}{16.9\%}
\newcommand{\daMeanSecurityPerc}{$16.9 \pm 0.0\%$}
\newcommand{\daMeanSecurityPercTwosfNominal}{17\%}
\newcommand{\daMeanSecurityPercTwosf}{$17 \pm 0\%$}
\newcommand{\daVulnFreeNominal}{0.169}
\newcommand{\daVulnFree}{$0.169 \pm 0.0$}
\newcommand{\daMeanOutstandingVulnerabilities}{$0.468 \pm 0.0$}
\newcommand{\daUpdatednessNominal}{0.0567}
\newcommand{\daUpdatedness}{$0.0567 \pm 0.0$}
\newcommand{\daUpdatednessPercNominal}{5.67\%}
\newcommand{\daUpdatednessPerc}{$5.67 \pm 0.0\%$}
\newcommand{\daUpdatednessPercTwosfNominal}{5.7\%}
\newcommand{\daUpdatednessPercTwosf}{$5.7 \pm 0.0\%$}
\newcommand{\daSecurityScoreNominal}{3.16}
\newcommand{\daSecurityScore}{$3.16 \pm 0.0$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{63.7\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$63.7 \pm 0.0\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{64\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$64 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{36.3\%}
\newcommand{\daCurrentMeanSecurityPerc}{$36.3 \pm 0.0\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{36\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$36 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.363}
\newcommand{\daCurrentVulnFree}{$0.363 \pm 0.0$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.0257 \pm 0.0$}
\newcommand{\daCurrentUpdatednessNominal}{0.0963}
\newcommand{\daCurrentUpdatedness}{$0.0963 \pm 0.0$}
\newcommand{\daCurrentUpdatednessPercNominal}{9.63\%}
\newcommand{\daCurrentUpdatednessPerc}{$9.63 \pm 0.0\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{9.6\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$9.6 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{4.7}
\newcommand{\daCurrentSecurityScore}{$4.7 \pm 0.0$}
\newcommand{\daDailyParticipationNominal}{885}
\newcommand{\daDailyParticipation}{$885 \pm 340$}
\newcommand{\daNumFullVersions}{1\,660}
\newcommand{\daNumSigFullVersions}{117}
\newcommand{\daNumOSVersions}{55}
\newcommand{\daNumSigOSVersions}{30}
\newcommand{\daNumAPIVersions}{17}
\newcommand{\daNumFullVersionUpdates}{5\,970}
\newcommand{\daNumOSVersionUpdates}{4\,310}
\newcommand{\daUpdatesPerYearNominal}{1.43}
\newcommand{\daUpdatesPerYear}{$1.43 \pm 0.01$}
\newcommand{\daUpdatesPerYearTwosfNominal}{1.4}
\newcommand{\daUpdatesPerYearTwosf}{$1.4 \pm 0.0$}
\newcommand{\daNumFullOnlyVersionUpdates}{1\,650}
\newcommand{\daNumSecurityUpdates}{1\,460}
\newcommand{\daNumPossibleSecurityUpdates}{2\,340}
\newcommand{\daOSCurveFitParamFirst}{81.0}
\newcommand{\daOSCurveFitParamSecond}{\num{0.00277}}
\newcommand{\daOSCurveFitRMSE}{0.109}
\newcommand{\daOSCurvePolyRMSE}{0.109}
\newcommand{\daOSCurveSplineRMSE}{0.109}

@@

\newcommand{\daOSCurveHalfDeployedYears}{$0.908 \pm 0.243$}

@@

\newcommand{\daOSCurveHalfDeployed}{$332 \pm 88$}
\newcommand{\daOSCurveFullDeployedYearsNominal}{3.19}
\newcommand{\daOSCurveFullDeployedYears}{$3.19 \pm 73$}
\newcommand{\daOSCurveFullDeployedNominal}{1\,160}
\newcommand{\daOSCurveFullDeployed}{$1\,160 \pm 268\,000$}
\newcommand{\daAPICurveFitParamFirst}{96.9}

@@

\newcommand{\daAPICurveFitRMSE}{0.106}
\newcommand{\daAPICurvePolyRMSE}{0.107}
\newcommand{\daAPICurveSplineRMSE}{0.107}
\newcommand{\daAPICurveHalfDeployedYearsNominal}{0.943}
\newcommand{\daAPICurveHalfDeployedYears}{$0.943 \pm 0.232$}
\newcommand{\daAPICurveHalfDeployedNominal}{344}
\newcommand{\daAPICurveHalfDeployed}{$344 \pm 84$}
\newcommand{\daAPICurveFullDeployedYearsNominal}{3.19}
\newcommand{\daAPICurveFullDeployedYears}{$3.19 \pm 72$}

@@

\newcommand{\daAPICurveFullDeployed}{$1\,170 \pm 264\,000$}
\newcommand{\daVulnAPKDuplicateFileOctoberPerc}{92.2\%}
\newcommand{\daVulnZergRushMonthsDefFixDeployed}{27.6}
\newcommand{\daTabSecScoresmanufacturer}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.44 \pm 0.00$ & $0.33 \pm 0.00$ & $0.55 \pm 0.01$ & $4.93 \pm 0.02$ \\  oneplus & $0.88 \pm 0.00$ & $0.31 \pm 0.01$ & $6.95 \pm 0.12$ & $4.44 \pm 0.03$ \\  Motorola & $0.32 \pm 0.00$ & $0.14 \pm 0.00$ & $0.65 \pm 0.01$ & $3.74 \pm 0.02$ \\  Sony & $0.29 \pm 0.00$ & $0.18 \pm 0.00$ & $1.06 \pm 0.02$ & $3.25 \pm 0.02$ \\  Samsung & $0.15 \pm 0.00$ & $0.06 \pm 0.00$ & $0.55 \pm 0.00$ & $2.95 \pm 0.00$ \\  HTC & $0.13 \pm 0.00$ & $0.09 \pm 0.00$ & $0.81 \pm 0.01$ & $2.66 \pm 0.02$ \\  Asus & $0.31 \pm 0.00$ & $0.46 \pm 0.01$ & $5.60 \pm 0.06$ & $2.64 \pm 0.02$ \\  \textit{other} & $0.05 \pm 0.00$ & $0.05 \pm 0.00$ & $0.97 \pm 0.01$ & $2.03 \pm 0.02$ \\  alps & $0.02 \pm 0.00$ & $0.20 \pm 0.01$ & $5.00 \pm 0.10$ & $0.73 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.10 \pm 0.00$ & $5.45 \pm 0.06$ & $0.33 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.09 \pm 0.00$ & $6.08 \pm 0.08$ & $0.28 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table*}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{4.93}
\newcommand{\daSecScoreBestmanufacturerScore}{$4.93 \pm 0.0$}
\newcommand{\daSecScoreBestmanufacturerNumFullVersions}{242}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.284}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.284 \pm 0.008$}
\newcommand{\daSecScoreWorstmanufacturerNumFullVersions}{22}
\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|l|c|c|c|c} Made by & Model name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & Nexus 5 & $0.78 \pm 0.00$ & $0.65 \pm 0.01$ & $6.02 \pm 0.09$ & $5.10 \pm 0.03$ \\  Samsung & Galaxy Nexus & $0.51 \pm 0.00$ & $0.53 \pm 0.01$ & $1.50 \pm 0.04$ & $4.75 \pm 0.05$ \\  LG & Nexus 4 & $0.60 \pm 0.00$ & $0.57 \pm 0.01$ & $5.52 \pm 0.08$ & $4.16 \pm 0.03$ \\  Asus & Nexus 7 & $0.46 \pm 0.00$ & $0.67 \pm 0.01$ & $5.69 \pm 0.08$ & $3.87 \pm 0.03$ \\  \textit{unknown} & \textit{other} & $0.14 \pm 0.00$ & $0.13 \pm 0.00$ & $0.54 \pm 0.00$ & $3.15 \pm 0.00$ \\  HTC & HTC Desire & $0.14 \pm 0.00$ & $0.07 \pm 0.01$ & $0.51 \pm 0.03$ & $3.03 \pm 0.05$ \\  HTC & Desire HD & $0.09 \pm 0.00$ & $0.05 \pm 0.00$ & $0.43 \pm 0.03$ & $2.86 \pm 0.04$ \\  Samsung & GT-I9000 & $0.03 \pm 0.00$ & $0.03 \pm 0.00$ & $0.44 \pm 0.04$ & $2.55 \pm 0.05$ \\  HTC & HTC Sensation & $0.34 \pm 0.00$ & $0.01 \pm 0.01$ & $1.49 \pm 0.06$ & $2.49 \pm 0.06$ \\  Motorola & DROIDX & $0.02 \pm 0.00$ & $0.04 \pm 0.01$ & $0.55 \pm 0.04$ & $2.39 \pm 0.06$ \\  Samsung & GT-I9100 & $0.21 \pm 0.00$ & $0.01 \pm 0.00$ & $1.26 \pm 0.02$ & $2.23 \pm 0.02$ \\  HTC & HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.08$ & $1.75 \pm 0.09$ \\  HTC & HTC One & $0.10 \pm 0.00$ & $0.38 \pm 0.01$ & $5.75 \pm 0.12$ & $1.56 \pm 0.04$ \\  Samsung & GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $2.46 \pm 0.05$ & $1.46 \pm 0.03$ \\  Samsung & GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $1.87 \pm 0.06$ & $0.84 \pm 0.05$ \\  Samsung & GT-I9505 & $0.10 \pm 0.00$ & $0.13 \pm 0.00$ & $6.79 \pm 0.07$ & $0.79 \pm 0.02$ \\  Samsung & SM-N9005 & $0.07 \pm 0.00$ & $0.15 \pm 0.01$ & $7.17 \pm 0.18$ & $0.72 \pm 0.03$ \\  Samsung & GT-I9300 & $0.14 \pm 0.00$ & $0.02 \pm 0.00$ & $6.26 \pm 0.05$ & $0.63 \pm 0.01$ \\  HTC & HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $3.03 \pm 0.05$ & $0.28 \pm 0.03$ \\  Samsung & GT-N7100 & $0.05 \pm 0.00$ & $0.00 \pm 0.01$ & $6.64 \pm 0.09$ & $0.21 \pm 0.02$ \\  Symphony & Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $11.00 \pm 0.13$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}
\newcommand{\daSecScoreBestmodel}{Nexus 5}
\newcommand{\daSecScoreBestmodelScoreNominal}{5.1}
\newcommand{\daSecScoreBestmodelScore}{$5.1 \pm 0.0$}
\newcommand{\daSecScoreBestmodelNumFullVersions}{47}

@@

\newcommand{\daSecScoreWorstmodelScore}{$0.0001 \pm 0.0283$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Nexus devices & $0.62 \pm 0.00$ & $0.50 \pm 0.00$ & $0.50 \pm 0.01$ & $6.26 \pm 0.02$ \\  non-Nexus & $0.13 \pm 0.00$ & $0.02 \pm 0.00$ & $0.54 \pm 0.00$ & $2.81 \pm 0.00$ \\ \end{tabular} \caption{Security scores for Nexus} \label{tab:sec_summary} \end{table*}}
\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline T-Mobile & $0.31 \pm 0.00$ & $0.17 \pm 0.00$ & $0.35 \pm 0.01$ & $4.24 \pm 0.02$ \\  O2 uk & $0.31 \pm 0.00$ & $0.12 \pm 0.00$ & $0.30 \pm 0.01$ & $4.15 \pm 0.02$ \\  Sprint & $0.23 \pm 0.00$ & $0.12 \pm 0.00$ & $0.30 \pm 0.01$ & $3.85 \pm 0.02$ \\  Orange & $0.23 \pm 0.00$ & $0.11 \pm 0.00$ & $0.34 \pm 0.02$ & $3.75 \pm 0.04$ \\  3 & $0.24 \pm 0.00$ & $0.11 \pm 0.00$ & $0.36 \pm 0.02$ & $3.72 \pm 0.03$ \\  AT\&T & $0.20 \pm 0.00$ & $0.09 \pm 0.00$ & $0.37 \pm 0.01$ & $3.53 \pm 0.02$ \\  Verizon & $0.25 \pm 0.00$ & $0.08 \pm 0.00$ & $0.58 \pm 0.01$ & $3.38 \pm 0.02$ \\  \textit{unknown} & $0.18 \pm 0.00$ & $0.19 \pm 0.00$ & $0.73 \pm 0.01$ & $3.26 \pm 0.02$ \\  Vodafone uk & $0.14 \pm 0.00$ & $0.14 \pm 0.00$ & $0.54 \pm 0.03$ & $3.18 \pm 0.04$ \\  n Telenor & $0.09 \pm 0.00$ & $0.13 \pm 0.00$ & $1.17 \pm 0.02$ & $2.19 \pm 0.02$ \\  Airtel & $0.05 \pm 0.00$ & $0.04 \pm 0.00$ & $2.48 \pm 0.04$ & $0.78 \pm 0.02$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.72 \pm 0.03$ & $0.51 \pm 0.01$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $3.13 \pm 0.05$ & $0.50 \pm 0.02$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $3.12 \pm 0.05$ & $0.37 \pm 0.01$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}
\newcommand{\daSecScoreBestoperator}{T-Mobile}
\newcommand{\daSecScoreBestoperatorScoreNominal}{4.24}
\newcommand{\daSecScoreBestoperatorScore}{$4.24 \pm 0.0$}
\newcommand{\daSecScoreBestoperatorNumFullVersions}{201}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.366}
\newcommand{\daSecScoreWorstoperatorScore}{$0.366 \pm 0.013$}
\newcommand{\daSecScoreWorstoperatorNumFullVersions}{76}
\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & Nexus \\ \hline equal & 0.0 & 0.0476 & 0.0714 & 0.0 \\weight $u$ & 0.0909 & 0.0952 & 0.143 & 0.0 \\weight $m$ & 0.273 & 0.286 & 0.0714 & 0.0 \\$f$ & 0.273 & 0.81 & 0.357 & 0.0 \\$m$ & 0.636 & 0.857 & 0.429 & 0.0 \\$u$ & 0.818 & 0.714 & 0.786 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
